\documentclass[11pt]{article}
\input{style.tex}

\begin{document}

\begin{center}
    {\Huge\bfseries\uppercase{Harikrishna Mekala}} \\ \medskip
    {\large Senior Software Engineer with 7+ years of experience in building scalable backend systems and cloud infrastructure.} \\ \medskip
    \href{mailto:me@hkmekala.me}{me@hkmekala.me} \quad
    \href{tel:+919177251060}{+91-9177251060} \quad
    \href{https://www.linkedin.com/in/hkmekala}{linkedin.com/in/hkmekala}
\end{center}

\section{Experience}
%=================%
\subsection{\textbf{KeenAi Global} - Senior Associate \rside{May 2025 - Present} \rside{Hybrid, Bangalore}}
\begin{itemize}
    \item Developed key features for Pulse, KeenAi's flagship wealth management product, focusing on backend services and data processing.
    \item Built Vault, a Dropbox-like internal file storage system, to enable secure, efficient, and auditable file management for Family Offices.
    \item Executed a full-stack migration of the backend from Spring Boot (Java) to NestJS (TypeScript), improving system scalability and developer velocity.
    \item Led the database migration from MySQL to MongoDB, ensuring complete data integrity, performance tuning, and zero downtime.
\end{itemize}

\subsection{\textbf{PayPal} - Software Engineer 3 \rside{September 2024 - May 2025} \rside{Hybrid, Bangalore}}
\begin{itemize}
	\item Engineered and scaled Large Language Model (LLM) inference and training infrastructure to support high-throughput AI services on the AI/ML Platform.
    \item Significantly enhanced the Data Loss Prevention (DLP) system, strengthening data security, risk management, and regulatory compliance.
    \item Developed a new, scalable LLM Platform to integrate Azure OpenAI models, enabling the processing of complex audio, image, and text data.
    \item Implemented sophisticated context management and hot-switching capabilities across Gemini, ChatGPT, and Claude models for optimal performance.
\end{itemize}

\subsection{\textbf{PayPal} - Software Engineer 2 \rside{June 2023 - August 2024} \rside{Hybrid, Chennai}}
\begin{itemize}
	\item Spearheaded the migration of a legacy C++ codebase to a modern Java Spring Boot framework, improving maintainability and code quality.
	\item Led the reengineering and cloud migration of the PayPal Payments settlement infrastructure from on-premises to AWS Cloud (DynamoDB, EKS).
    \item Built a real-time snapshotting solution to accelerate bank settlements, reducing processing time and improving transaction throughput.
    \item Served as Scrum Master, championing Agile methodologies to ensure on-time project delivery and continuous improvement.
\end{itemize}

\subsection{\textbf{smallcase} - Software Development Engineer 1 \rside{April 2022 - May 2023} \rside{Remote, Bangalore}}
\begin{itemize}
    \item Developed backend microservices to rank equity mutual funds based on market capitalization and fund allocation.
    \item Integrated 24 new indices into the Tickertape platform, providing comprehensive real-time sector tracking.
    \item Implemented proprietary algorithms for calculating PE ratios and portfolio volatility, enhancing financial data analysis capabilities.
    \item Designed and created a highly available, low-latency stock Scorecard REST API, serving over 4.5 million active users.
    \item Transitioned Tickertape’s core API to a new pod-level segregation architecture using NestJS for improved isolation and stability.
\end{itemize}

\subsection{\textbf{Aardwolf Security} - Software Engineer \rside{November 2019 - March 2022} \rside{Remote, London}}
\begin{itemize}
    \item Built a highly available, fault-tolerant content ranking system with a customer-facing REST API.
    \item Developed a high-throughput parsing engine for scraping, processing, and ranking content from blog RSS feeds.
    \item Established a complete CI/CD pipeline using Jenkins and SonarQube, automating the build, test, and deployment lifecycle.
    \item Created a full-featured affiliate system for user referrals with integrated PayPal Payouts API.
    \item Implemented automated, firewall-based traffic throttling to effectively mitigate DDoS attacks and ensure service availability.
    \item Designed a robust queuing mechanism for large-scale, asynchronous content analysis using a manager-worker model.
\end{itemize}

\subsection{\textbf{Kloudgin} - Software Engineer \rside{July 2019 - November 2019} \rside{Office, Hyderabad}}
\begin{itemize}
    \item Architected and implemented a modular Netsuite integration package for the Kloudgin Field Service Management (FSM) platform.
    \item Engineered a distributed, multi-threaded system to execute large-scale, mission-critical enterprise data migrations.
\end{itemize}

\subsection{\textbf{Infovity} - Technical Consultant \rside{May 2018 - July 2019} \rside{Office, Hyderabad}}
\begin{itemize}
    \item As a contractor for Kloudgin, implemented video streaming capabilities for their crew training module, enhancing user engagement.
    \item Developed a Java iText Library wrapper to enable custom PDF invoice generation within the Kloudgin application.
    \item Architected and built a Docker-based microservices application to automate tracking of internal employee billables and biometrics.
\end{itemize}

\section{Education}
%=================%
\subsection{Vishnu Institute of Technology \aux{Computer Science and Engineering} \rside{2018}}
\begin{itemize}
    \item Cumulative Percentage: 72\% \textit{(Distinction)}
    \item Awarded 1st place in the VEDIC Inter-Collegiate Coding Competition.
    \item Developed a containerized code compiler to facilitate secure remote code execution for university platforms.
    \item Built the real-time ranking system for the annual college coding competition.
    \item Co-developed an automatic lab record generation plugin for the Moodle LMS.
\end{itemize}

\section{Skills \& Interests}
%===========================%
\begin{description}
    \item[Core Competencies] System Design, Microservices Architecture, Cloud Native Development, Data Structures, Algorithms, Agile/Scrum Methodologies, DevOps Practices, CI/CD, Performance Tuning
    \item[Languages \& Frameworks] Java (Spring Boot), Python, Node.JS (NestJS), TypeScript, Go, Shell Scripting
    \item[Databases \& Messaging] MongoDB, DynamoDB, SQL (MySQL), Redis, Kafka
    \item[Tools \& Platforms] AWS, Docker, Kubernetes (EKS), Jenkins, Git, Jira, Postman, SonarQube
    \item[Interests] Building custom PC workstations and contributing to open-source projects.
\end{description}

\end{document}