\documentclass[11pt]{article}
\usepackage{enumitem} % For list presentation
\input{style.tex}

\begin{document}

\begin{center}
    {\Huge\bfseries\uppercase{Harikrishna Mekala}} \\ \medskip
    {\large Senior Software Engineer | 7+ Years Experience | Backend & Cloud Systems} \\ \medskip
    \href{mailto:me@hkmekala.me}{me@hkmekala.me} \quad
    \href{tel:+919177251060}{+91-9177251060} \quad
    \href{https://www.linkedin.com/in/hkmekala}{linkedin.com/in/hkmekala}
\end{center}

\section{Experience}
%=================%
\subsection{\textbf{KeenAi Global} - Senior Associate \rside{May 2025 - Present} \rside{Hybrid, Bangalore}}
\begin{itemize}[nosep, leftmargin=*]
    \item Developed key backend features for KeenAi's flagship product (Pulse) and built Vault, a secure internal file storage system for Family Offices.
    \item Executed a full-stack migration of the backend from Spring Boot (Java) to NestJS (TypeScript), improving system scalability and developer velocity.
\end{itemize}

\subsection{\textbf{PayPal} - Software Engineer (SE2 / SE3) \rside{June 2023 - May 2025} \rside{Hybrid, Bangalore & Chennai}}
\begin{itemize}[nosep, leftmargin=*]
    \item Promoted to Software Engineer 3, transitioning from the Payments team to the AI/ML Platform team to lead new initiatives.
    \item Modernized the PayPal Payments infrastructure by migrating a legacy C++ codebase to Java Spring Boot and reengineering settlement systems to AWS Cloud.
    \item Engineered and scaled LLM training and inference infrastructure to support high-throughput AI services.
    \item Developed a new platform to integrate Azure OpenAI models, enabling advanced processing of audio, image, and text data.
    \item Significantly enhanced the Data Loss Prevention (DLP) system, strengthening data security and compliance.
\end{itemize}

\subsection{\textbf{smallcase} - Software Development Engineer 1 \rside{April 2022 - May 2023} \rside{Remote, Bangalore}}
\begin{itemize}[nosep, leftmargin=*]
    \item Developed backend microservices for financial analysis, integrating 24 indices and implementing algorithms for fund ranking, PE ratios, and volatility.
    \item Designed a highly available, low-latency stock Scorecard REST API (serving 4.5M+ users) and transitioned its architecture for improved stability.
\end{itemize}

\subsection{\textbf{Aardwolf Security} - Software Engineer \rside{November 2019 - March 2022} \rside{Remote, London}}
\begin{itemize}[nosep, leftmargin=*]
    \item Built a highly available, fault-tolerant content ranking system with a high-throughput parsing engine for blog RSS feeds.
    \item Established a complete CI/CD pipeline (Jenkins, SonarQube) and implemented automated firewall-based throttling to mitigate DDoS attacks.
    \item Created a full-featured affiliate system with PayPal Payouts integration and designed a robust queuing mechanism for asynchronous content analysis.
\end{itemize}

\subsection{\textbf{Infovity} - Technical Consultant \rside{May 2018 - November 2019} \rside{Office, Hyderabad}}
\begin{itemize}[nosep, leftmargin=*]
    \item As a consultant assigned to client Kloudgin, designed and implemented a modular Netsuite integration package for their FSM platform.
    \item Developed a distributed, multi-threaded system for large-scale enterprise data migration for the client.
    \item Added video streaming support and a Java iText wrapper for custom PDF invoice generation within the Kloudgin application.
    \item Architected an internal, Docker-based microservices application at Infovity to automate employee billables tracking.
\end{itemize}

\section{Education}
%=================%
\subsection{Vishnu Institute of Technology \aux{Computer Science and Engineering} \rside{2018}}
\begin{itemize}[nosep, leftmargin=*]
    \item Cumulative Percentage: 72\% (Distinction); 1st place in VEDIC Coding Competition; Key projects included a containerized compiler, a real-time ranking system, and a Moodle plugin.
\end{itemize}

\section{Skills \& Interests}
%===========================%
\begin{description}[nosep, leftmargin=*, style=unboxed]
    \item[Core Competencies] System Design, Microservices Architecture, Cloud Native Development, Data Structures, Algorithms, Agile/Scrum Methodologies, DevOps Practices, CI/CD, Performance Tuning
    \item[Languages & Frameworks] Java (Spring Boot), Python, Node.JS (NestJS), TypeScript, Go, Shell Scripting
    \item[Databases \& Messaging] MongoDB, DynamoDB, SQL (MySQL), Redis, Kafka
    \item[Tools \& Platforms] AWS, Docker, Kubernetes (EKS), Jenkins, Git, Jira, Postman, SonarQube
    \item[Interests] Building custom PC workstations and contributing to open-source projects.
\end{description}

\end{document}