\section{Experience}
%=================%

\subsection{\role{KeenAi Global}{Senior Associate}{May 2025 - Present}{Hybrid, Bangalore}}
\begin{itemize}
    \bb{Architected and shipped a \textbf{Trading Backend} routing flows across \textbf{23 global exchanges} (US, Europe, Singapore) and broker-dealers (\textbf{Pershing / NetX360}) over the \textbf{FIX Protocol} for institutional equity, options, and OTC structured products.}
    \bb{Built an end-to-end \textbf{real-time order lifecycle} pipeline --- placement, ack, partial-fill, execution report, allocation, settlement --- with idempotent state machines and exactly-once event semantics on \textbf{AWS SQS}.}
    \bb{Designed and built the \textbf{Derivatives Market} data layer on MongoDB --- the source-of-truth for \textbf{custom OTC instruments} (FCNs, structured notes) --- exposing listings, quote-currency, LCM, issuer credit rating, and risk APIs.}
    \bb{Engineered a \textbf{fault-tolerant Pershing webhooks} ingestion pipeline (API Gateway + ACM + SQS FIFO + EventBridge) with at-least-once delivery, DLQ handling, and replay --- provisioned end-to-end with \textbf{Terraform}.}
    \bb{Owned the \textbf{FIX execution-report consumer} for OTC FCN trades, reconciling \textbf{back-to-back NetX360 $\leftrightarrow$ Pershing} flows and matching trade state across upstream brokers and downstream books.}
    \fb{Executed a \textbf{full-stack platform rewrite} from \textbf{Spring Boot + MySQL} to \textbf{NestJS + MongoDB} with zero downtime, unifying the runtime and dramatically improving developer velocity and query performance.}
    \fb{Authored \textbf{Temporal workflows} for long-running structured-product lifecycle events (issuance, coupon payments, knock-in / knock-out, early redemption) with deterministic retries, durable state, and human-in-the-loop escalation.}
    \fb{Built a low-latency in-memory \textbf{trie + scored-cache} search engine over the global instrument universe, returning \textbf{sub-100\,ms} ranked suggestions across \textbf{millions of instruments}.}
    \fb{Replaced legacy hardcoded keys with a \textbf{Cognito-backed service-to-service auth} layer, centralizing credential issuance, rotation, and audit across internal microservices.}
    \fb{Built \textbf{Vault}, a secure Dropbox-like internal file-storage system with \textbf{fine-grained RBAC}, per-Family-Office tenancy, audit logs, and signed-URL delivery for institutional clients.}
\end{itemize}

\subsection{\role{PayPal}{Software Engineer 3}{September 2024 - May 2025}{Hybrid, Bangalore}}
\begin{itemize}
    \bb{Owned the \textbf{OpenAI LLM Gateway} within the \textbf{PayPal Cosmos} AI/ML Platform, scaling \textbf{multi-tenant inference, training, and Agentic AI} infrastructure to \textbf{1M+ AI calls} across PayPal's product surfaces.}
    \bb{Built a unified \textbf{LLM Platform} integrating \textbf{Azure OpenAI}, enabling production-grade processing of audio, image, and text data for fraud detection, risk scoring, and customer support.}
    \bb{Hardened the \textbf{Data Loss Prevention (DLP)} system, strengthening data security, risk management, and regulatory compliance across PayPal's enterprise data surfaces.}
    \fb{Implemented \textbf{multi-model context management and hot-switching} across \textbf{Gemini, ChatGPT, and Claude} with request-time routing for cost / latency / quality tradeoffs.}
\end{itemize}

\subsection{\role{PayPal}{Software Engineer 2}{June 2023 - August 2024}{Hybrid, Chennai}}
\begin{itemize}
    \fb{Led the reengineering and \textbf{AWS cloud migration} of PayPal's \textbf{Payments settlement infrastructure} (\textbf{\$1T+ annual TPV}) from on-prem to a fault-tolerant distributed system on \textbf{DynamoDB + EKS}.}
    \fb{Built a \textbf{real-time snapshotting} solution to accelerate bank settlements, reducing end-of-day processing time and improving daily transaction throughput.}
    \fb{Spearheaded the migration of a legacy \textbf{C++ codebase to Java Spring Boot}, modernizing a critical settlement component and improving maintainability.}
    \fb{Served as \textbf{Scrum Master} for PayPal's \textbf{Payments Cloud Migration Team}, driving Agile delivery and continuous improvement throughout the on-prem-to-AWS reengineering.}
    \mb{Led PayPal's \textbf{Payments settlement} \textbf{AWS cloud migration} at \textbf{\$1T+ TPV scale} from on-prem to a fault-tolerant distributed system on \textbf{DynamoDB + EKS}, and built a \textbf{real-time snapshotting} layer that accelerated bank settlements and improved daily throughput.}
\end{itemize}

\subsection{\role{smallcase}{Software Development Engineer 1}{April 2022 - May 2023}{Remote, Bangalore}}
\begin{itemize}
    \fb{Designed a highly available, \textbf{low-latency Stock Scorecard REST API} serving \textbf{4.5M+ active users}, powering Tickertape's flagship equity-research surface.}
    \fb{Implemented proprietary algorithms for \textbf{PE ratios, portfolio volatility, and equity-fund ranking} by market cap and allocation --- feeding Tickertape's screener and recommendation engine.}
    \fb{Integrated \textbf{24 new market indices} for real-time sector tracking and added regular Mutual Fund coverage, expanding the platform's tradable universe by \textbf{50\%}.}
    \fb{Built internal \textbf{gRPC} services with \textbf{LRU-cache}-backed hot paths to scale Scorecard fan-out to \textbf{millions of requests/day}.}
    \fb{Led the migration of Tickertape's core API to a \textbf{pod-level segregated NestJS architecture} for fault isolation and stability.}
    \mb{Designed a \textbf{low-latency Stock Scorecard REST API} serving \textbf{4.5M+ active users} on Tickertape, with proprietary algorithms for \textbf{PE ratios, portfolio volatility, and equity-fund ranking} powering the screener and recommendation engine.}
\end{itemize}

% ------- Aardwolf: full-only, hidden in min -------
\fonly{%
\subsection{\role{Aardwolf Security}{Software Engineer}{November 2019 - March 2022}{Remote, London}}
\begin{itemize}
    \item Built a highly available, \textbf{fault-tolerant content ranking system} with a customer-facing REST API and a high-throughput RSS parsing engine.
    \item Established the full \textbf{CI/CD pipeline} (Jenkins + SonarQube) and implemented automated \textbf{firewall-based traffic throttling} to mitigate DDoS attacks.
    \item Built a \textbf{PayPal Payouts}-backed affiliate system and designed a \textbf{manager-worker queuing system} for large-scale asynchronous content analysis.
\end{itemize}
}

% ------- Earlier roles: full only, dropped from min -------
\fonly{%
\subsection{\role{Kloudgin}{Software Engineer}{July 2019 - November 2019}{Office, Hyderabad}}
\begin{itemize}
    \item Architected a modular \textbf{Netsuite integration} for the FSM platform and engineered a \textbf{distributed multi-threaded data-migration} system for enterprise customers.
\end{itemize}

\subsection{\role{Infovity}{Technical Consultant}{May 2018 - July 2019}{Office, Hyderabad}}
\begin{itemize}
    \item Contracted to Kloudgin: added video-streaming for crew training, built a \textbf{Java iText} wrapper for custom PDF invoices, and shipped a \textbf{Docker-based microservices} app for billables / biometrics tracking.
\end{itemize}
}
